Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Petersburg version \YellowPaperVersionNumber}}

### 2020-05-10 Paper.tex
EIP 1014: Skinny CREATE2

Evaluating $\boldsymbol{\sigma}_{P}$ from $\boldsymbol{\sigma}_0$ depends on the transaction type; either contract creation or message call; we define the tuple of post-execution provisional state $\boldsymbol{\sigma}_{P}$, remaining gas $g'$, accrued substate $A$ and status code $z$:
\begin{equation}
(\boldsymbol{\sigma}_{P}, g', A, z) \equiv \begin{cases}
\Lambda_{4}(\boldsymbol{\sigma}_0, S(T), T_{\mathrm{o}}, g, &\\ \quad\quad T_{\mathrm{p}}, T_{\mathrm{v}}, T_{\mathbf{i}}, 0, \top) & \text{if} \quad T_{\mathrm{t}} = \varnothing \\
\Theta_{4}(\boldsymbol{\sigma}_0, S(T), T_{\mathrm{o}}, T_{\mathrm{t}}, T_{\mathrm{t}}, &\\ \quad\quad g, T_{\mathrm{p}}, T_{\mathrm{v}}, T_{\mathrm{v}}, T_{\mathbf{d}}, 0, \top) & \text{otherwise}
\end{cases}
\end{equation}

@@

There are a number of intrinsic parameters used when creating an account: sender ($s$), original transactor ($o$), available gas ($g$), gas price ($p$), endowment ($v$) together with an arbitrary length byte array, $\mathbf{i}$, the initialisation EVM code, the present depth of the message-call/contract-creation stack ($e$) and finally the permission to make modifications to the state ($w$).

We define the creation function formally as the function $\Lambda$, which evaluates from these values, together with the state $\boldsymbol{\sigma}$ to the tuple containing the new state, remaining gas, accrued transaction substate and an error message $(\boldsymbol{\sigma}', g', A, \mathbf{o})$, as in section \ref{ch:transactions}:
\begin{equation}
(\boldsymbol{\sigma}', g', A, z, \mathbf{o}) \equiv \Lambda(\boldsymbol{\sigma}, s, o, g, p, v, \mathbf{i}, e, w)
\end{equation}

The address of the new account is defined as being the rightmost 160 bits of the Keccak hash of the \hyperlink{rlp}{RLP} encoding of the structure containing only the sender and the \hyperlink{account_nonce}{account nonce}. Thus we define the resultant address for the new account $a$:
\begin{equation}
a \equiv \mathcal{B}_{96..255}\Big(\mathtt{KEC}\Big(\mathtt{RLP}\big(\;(s, \boldsymbol{\sigma}[s]_{\mathrm{n}} - 1)\;\big)\Big)\Big)
\end{equation}

where $\mathtt{KEC}$ is the Keccak 256-bit hash function, $\mathtt{RLP}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to a binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$, and $\boldsymbol{\sigma}[x]$ is the address state of $x$, or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

@@

Fees (denominated in gas) are charged under three distinct circumstances, all three as prerequisite to the execution of an operation. The first and most common is the fee intrinsic to the computation of the operation (see Appendix \ref{app:fees}). Secondly, gas may be deducted in order to form the payment for a subordinate message call or contract creation; this forms part of the payment for {\small CREATE}, {\small CALL} and {\small CALLCODE}. Finally, gas may be paid due to an increase in the usage of the memory.

@@

\begin{itemize}
\item\linkdest{address_of_account_which_owns_code_I__a_def_words}{}\linkdest{I__a} $I_{\mathrm{a}}$, the address of the account which owns the code that is executing.
\item\linkdest{address_of_sender_of_tx_that_originated_execution_I__o}{}\linkdest{I__o} $I_{\mathrm{o}}$, the sender address of the transaction that originated this execution.
\item\linkdest{gas_price_in_tx_that_originated_execution_I__p}{}\linkdest{I__p} $I_{\mathrm{p}}$, the price of gas in the transaction that originated this execution.
\item\linkdest{execution_input_data_I__d}{}\linkdest{I__d} $I_{\mathbf{d}}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item\linkdest{the_address_of_the_account_which_caused_the_code_to_be_executing_I__s}{} $I_{\mathrm{s}}$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item\linkdest{Wei_value_exec_I__v}{}\linkdest{I__v}{} $I_{\mathrm{v}}$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item\linkdest{exec_machine_code_I__b}{}\linkdest{I__b} $I_{\mathbf{b}}$, the byte array that is the machine code to be executed.
\item\linkdest{exec_block_header_I__H}{}\linkdest{I__H} $I_{\mathbf{H}}$, the block header of the present block.
\item\linkdest{exec_call_or_create_depth_I__e}{}\linkdest{I__e} $I_{\mathrm{e}}$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).
\item\linkdest{exec_permission_to_modify_state_I__w}{}\linkdest{I__w} $I_{\mathrm{w}}$, the permission to make modifications to the state.
\end{itemize}

@@

The exceptional halting function $Z$ is defined as:
\begin{equation}
Z(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \equiv
\begin{array}[t]{l}
\boldsymbol{\mu}_g < C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \quad \vee \\
\mathbf{\delta}_w = \varnothing \quad \vee \\
\lVert\boldsymbol{\mu}_\mathbf{s}\rVert < \mathbf{\delta}_w \quad \vee \\
( w = \text{\small JUMP} \quad \wedge \quad \boldsymbol{\mu}_\mathbf{s}[0] \notin D(I_\mathbf{b}) ) \quad \vee \\
( w = \text{\small JUMPI} \quad \wedge \quad \boldsymbol{\mu}_\mathbf{s}[1] \neq 0 \quad \wedge \\
\quad \boldsymbol{\mu}_\mathbf{s}[0] \notin D(I_\mathbf{b}) ) \quad \vee \\
( w = \text{\small RETURNDATACOPY} \wedge \\ \quad \boldsymbol{\mu}_{\mathbf{s}}[1] + \boldsymbol{\mu}_{\mathbf{s}}[2] > \lVert\boldsymbol{\mu}_{\mathbf{o}}\rVert) \quad \vee \\
\lVert\boldsymbol{\mu}_\mathbf{s}\rVert - \mathbf{\delta}_w + \mathbf{\alpha}_w > 1024 \vee
 (\neg I_{\mathrm{w}} \wedge W(w, \boldsymbol{\mu}))
\end{array}
\end{equation}
where
\begin{equation}
W(w, \boldsymbol{\mu}) \equiv \\
\begin{array}[t]{l}
w \in \{\text{\small CREATE}, \text{\small SSTORE},\\ \text{\small SELFDESTRUCT}\} \ \vee \\
\text{\small LOG0} \le w \wedge w \le \text{\small LOG4} \quad \vee \\
w \in \{\text{\small CALL}, \text{\small CALLCODE}\} \wedge \boldsymbol{\mu}_{\mathbf{s}}[2] \neq 0
\end{array}
\end{equation}

@@

\begin{equation}
C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \equiv C_{mem}(\boldsymbol{\mu}'_{\mathrm{i}})-C_{mem}(\boldsymbol{\mu}_{\mathrm{i}}) + \begin{cases}
C_\text{\tiny SSTORE}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small SSTORE} \\
G_{exp} & \text{if} \quad w = \text{\small EXP} \wedge \boldsymbol{\mu}_{\mathbf{s}}[1] = 0 \\
G_{exp} + G_{expbyte}\times(1+\lfloor\log_{256}(\boldsymbol{\mu}_{\mathbf{s}}[1])\rfloor) & \text{if} \quad w = \text{\small EXP} \wedge \boldsymbol{\mu}_{\mathbf{s}}[1] > 0 \\
G_{verylow} + G_{copy}\times\lceil\boldsymbol{\mu}_{\mathbf{s}}[2] \div 32\rceil & \text{if} \quad w = \text{\small CALLDATACOPY} \> \lor \\
&\quad\text{\small CODECOPY} \lor \text{\small RETURNDATACOPY} \\
G_{extcode} + G_{copy}\times\lceil\boldsymbol{\mu}_{\mathbf{s}}[3] \div 32\rceil & \text{if} \quad w = \text{\small EXTCODECOPY} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1] & \text{if} \quad w = \text{\small LOG0} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+G_{logtopic} & \text{if} \quad w = \text{\small LOG1} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+2G_{logtopic} & \text{if} \quad w = \text{\small LOG2} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+3G_{logtopic} & \text{if} \quad w = \text{\small LOG3} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+4G_{logtopic} & \text{if} \quad w = \text{\small LOG4} \\
C_\text{\tiny CALL}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small CALL} \lor \text{\small CALLCODE} \> \lor \\
&\quad\text{\small DELEGATECALL} \\
C_\text{\tiny SELFDESTRUCT}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small SELFDESTRUCT} \\
G_{create} & \text{if} \quad w = \text{\small CREATE}\\
G_{sha3}+G_{sha3word} \lceil \mathbf{s}[1] \div 32 \rceil & \text{if} \quad w = \text{\small SHA3}\\
G_{jumpdest} & \text{if} \quad w = \text{\small JUMPDEST}\\
G_{sload} & \text{if} \quad w = \text{\small SLOAD}\\
G_{zero} & \text{if} \quad w \in W_{zero}\\
G_{base} & \text{if} \quad w \in W_{base}\\
G_{verylow} & \text{if} \quad w \in W_{verylow}\\
G_{\mathrm{low}} & \text{if} \quad w \in W_{\mathrm{low}}\\
G_{mid} & \text{if} \quad w \in W_{mid}\\
G_{\mathrm{high}} & \text{if} \quad w \in W_{\mathrm{high}}\\
G_{extcode} & \text{if} \quad w = \text{\small EXTCODESIZE}\\
G_{extcodehash} & \text{if} \quad w = \text{\small \hyperlink{extcodehash}{EXTCODEHASH}}\\
G_{balance} & \text{if} \quad w = \text{\small BALANCE}\\
G_{blockhash} & \text{if} \quad w = \text{\small \hyperlink{blockhash}{BLOCKHASH}}\\
\end{cases}
\end{equation}
\begin{equation}
w \equiv \begin{cases} I_{\mathbf{b}}[\boldsymbol{\mu}_{\mathrm{pc}}] & \text{if} \quad \boldsymbol{\mu}_{\mathrm{pc}} < \lVert I_{\mathbf{b}} \rVert\\
\text{\small STOP} & \text{otherwise}
\end{cases}
\end{equation}

@@

&&&& $(\boldsymbol{\sigma}', \boldsymbol{\mu}'_{\mathrm{g}}, A^+, \mathbf{o}) \equiv \begin{cases}\Lambda(\boldsymbol{\sigma}^*, I_{\mathrm{a}}, I_{\mathrm{o}}, L(\boldsymbol{\mu}_{\mathrm{g}}), I_{\mathrm{p}}, \boldsymbol{\mu}_{\mathbf{s}}[0], \mathbf{i}, I_{\mathrm{e}} + 1, I_{\mathrm{w}}) & \text{if} \quad \boldsymbol{\mu}_{\mathbf{s}}[0] \leqslant \boldsymbol{\sigma}[I_{\mathrm{a}}]_{\mathrm{b}} \; \\ \quad &\wedge\; I_{\mathrm{e}} < 1024\\ \big(\boldsymbol{\sigma}, \boldsymbol{\mu}_{\mathrm{g}}, \varnothing\big) & \text{otherwise} \end{cases}$ \\
&&&& is too low to fulfil the value transfer); and otherwise $x=A(I_{\mathrm{a}}, \boldsymbol{\sigma}[I_{\mathrm{a}}]_{\mathrm{n}})$, the\\
&&&& address of the newly created account. \\
&&&& Thus the operand order is: value, input offset, input size. \\

@@

>>>>

Evaluating $\boldsymbol{\sigma}_{P}$ from $\boldsymbol{\sigma}_0$ depends on the transaction type; either contract creation or message call; we define the tuple of post-execution provisional state $\boldsymbol{\sigma}_{P}$, remaining gas $g'$, accrued substate $A$ and status code $z$:
\begin{equation}
(\boldsymbol{\sigma}_{P}, g', A, z) \equiv \begin{cases}
\Lambda_{4}(\boldsymbol{\sigma}_0, S(T), T_{\mathrm{o}}, g, &\\ \quad\quad T_{\mathrm{p}}, T_{\mathrm{v}}, T_{\mathbf{i}}, 0, \varnothing, \top) & \text{if} \quad T_{\mathrm{t}} = \varnothing \\
\Theta_{4}(\boldsymbol{\sigma}_0, S(T), T_{\mathrm{o}}, T_{\mathrm{t}}, T_{\mathrm{t}}, &\\ \quad\quad g, T_{\mathrm{p}}, T_{\mathrm{v}}, T_{\mathrm{v}}, T_{\mathbf{d}}, 0, \top) & \text{otherwise}
\end{cases}
\end{equation}

@@

There are a number of intrinsic parameters used when creating an account: sender ($s$), original transactor ($o$), available gas ($g$), gas price ($p$), endowment ($v$) together with an arbitrary length byte array, $\mathbf{i}$, the initialisation EVM code, the present depth of the message-call/contract-creation stack ($e$), the salt for new account's address ($\zeta$) and finally the permission to make modifications to the state ($w$).
The salt $\zeta$ might be missing ($\zeta = \varnothing$); formally,
\begin{equation}
\zeta \in \mathbb{B}_{32} \cup \mathbb{B}_{0}
\end{equation}
If the creation was caused by {\small \hyperlink{create2}{CREATE2}}, then $\zeta \neq \varnothing$.

We define the creation function formally as the function $\Lambda$, which evaluates from these values, together with the state $\boldsymbol{\sigma}$ to the tuple containing the new state, remaining gas, accrued transaction substate and an error message $(\boldsymbol{\sigma}', g', A, \mathbf{o})$, as in section \ref{ch:transactions}:
\begin{equation}
(\boldsymbol{\sigma}', g', A, z, \mathbf{o}) \equiv \Lambda(\boldsymbol{\sigma}, s, o, g, p, v, \mathbf{i}, e, \zeta, w)
\end{equation}

The address of the new account is defined as being the rightmost 160 bits of the Keccak hash of the \hyperlink{rlp}{RLP} encoding of the structure containing only the sender and the \hyperlink{account_nonce}{account nonce}.
For {\small \hyperlink{create2}{CREATE2}} the rule is different and is described in EIP-1014.
Combining the two cases, we define the resultant address for the new account $a$:
\begin{eqnarray}
a & \equiv & A(s, \boldsymbol{\sigma}[s]_{\mathrm{n}} - 1, \zeta, \mathbf{i}) \\
\label{eq:new-address} A(s, n, \zeta, \mathbf{i}) & \equiv & \mathcal{B}_{96..255}\Big(\mathtt{KEC}\big(B(s, n, \zeta, \mathbf{i})\big)\Big) \\
B(s, n, \zeta, \mathbf{i}) & \equiv & \begin{cases}
\mathtt{RLP}\big(\;(s, n)\;\big) & \text{if}\ \zeta = \varnothing \\
(255) \cdot s \cdot \zeta \cdot \mathtt{KEC}(\mathbf{i}) & \text{otherwise}
\end{cases}
\end{eqnarray}

where $\cdot$ is the concatenation of byte arrays, $\mathcal{B}_{a..b}(X)$ evaluates to a binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$, and $\boldsymbol{\sigma}[x]$ is the address state of $x$, or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

@@

Fees (denominated in gas) are charged under three distinct circumstances, all three as prerequisite to the execution of an operation. The first and most common is the fee intrinsic to the computation of the operation (see Appendix \ref{app:fees}). Secondly, gas may be deducted in order to form the payment for a subordinate message call or contract creation; this forms part of the payment for {\small CREATE}, {\small CREATE2}, {\small CALL} and {\small CALLCODE}. Finally, gas may be paid due to an increase in the usage of the memory.

@@

\begin{itemize}
\item\linkdest{address_of_account_which_owns_code_I__a_def_words}{}\linkdest{I__a} $I_{\mathrm{a}}$, the address of the account which owns the code that is executing.
\item\linkdest{address_of_sender_of_tx_that_originated_execution_I__o}{}\linkdest{I__o} $I_{\mathrm{o}}$, the sender address of the transaction that originated this execution.
\item\linkdest{gas_price_in_tx_that_originated_execution_I__p}{}\linkdest{I__p} $I_{\mathrm{p}}$, the price of gas in the transaction that originated this execution.
\item\linkdest{execution_input_data_I__d}{}\linkdest{I__d} $I_{\mathbf{d}}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item\linkdest{the_address_of_the_account_which_caused_the_code_to_be_executing_I__s}{} $I_{\mathrm{s}}$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item\linkdest{Wei_value_exec_I__v}{}\linkdest{I__v}{} $I_{\mathrm{v}}$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item\linkdest{exec_machine_code_I__b}{}\linkdest{I__b} $I_{\mathbf{b}}$, the byte array that is the machine code to be executed.
\item\linkdest{exec_block_header_I__H}{}\linkdest{I__H} $I_{\mathbf{H}}$, the block header of the present block.
\item\linkdest{exec_call_or_create_depth_I__e}{}\linkdest{I__e} $I_{\mathrm{e}}$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE(2)}s being executed at present).
\item\linkdest{exec_permission_to_modify_state_I__w}{}\linkdest{I__w} $I_{\mathrm{w}}$, the permission to make modifications to the state.
\end{itemize}

@@

The exceptional halting function $Z$ is defined as:
\begin{equation}
Z(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \equiv
\begin{array}[t]{l}
\boldsymbol{\mu}_g < C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \quad \vee \\
\mathbf{\delta}_w = \varnothing \quad \vee \\
\lVert\boldsymbol{\mu}_\mathbf{s}\rVert < \mathbf{\delta}_w \quad \vee \\
( w = \text{\small JUMP} \quad \wedge \quad \boldsymbol{\mu}_\mathbf{s}[0] \notin D(I_\mathbf{b}) ) \quad \vee \\
( w = \text{\small JUMPI} \quad \wedge \quad \boldsymbol{\mu}_\mathbf{s}[1] \neq 0 \quad \wedge \\
\quad \boldsymbol{\mu}_\mathbf{s}[0] \notin D(I_\mathbf{b}) ) \quad \vee \\
( w = \text{\small RETURNDATACOPY} \wedge \\ \quad \boldsymbol{\mu}_{\mathbf{s}}[1] + \boldsymbol{\mu}_{\mathbf{s}}[2] > \lVert\boldsymbol{\mu}_{\mathbf{o}}\rVert) \quad \vee \\
\lVert\boldsymbol{\mu}_\mathbf{s}\rVert - \mathbf{\delta}_w + \mathbf{\alpha}_w > 1024 \vee
 (\neg I_{\mathrm{w}} \wedge W(w, \boldsymbol{\mu}))
\end{array}
\end{equation}
where
\begin{equation}
W(w, \boldsymbol{\mu}) \equiv \\
\begin{array}[t]{l}
w \in \{\text{\small CREATE}, \text{\small CREATE2}, \text{\small SSTORE},\\ \text{\small SELFDESTRUCT}\} \ \vee \\
\text{\small LOG0} \le w \wedge w \le \text{\small LOG4} \quad \vee \\
w \in \{\text{\small CALL}, \text{\small CALLCODE}\} \wedge \boldsymbol{\mu}_{\mathbf{s}}[2] \neq 0
\end{array}
\end{equation}

@@

\begin{equation}
C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \equiv C_{mem}(\boldsymbol{\mu}'_{\mathrm{i}})-C_{mem}(\boldsymbol{\mu}_{\mathrm{i}}) + \begin{cases}
C_\text{\tiny SSTORE}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small SSTORE} \\
G_{exp} & \text{if} \quad w = \text{\small EXP} \wedge \boldsymbol{\mu}_{\mathbf{s}}[1] = 0 \\
G_{exp} + G_{expbyte}\times(1+\lfloor\log_{256}(\boldsymbol{\mu}_{\mathbf{s}}[1])\rfloor) & \text{if} \quad w = \text{\small EXP} \wedge \boldsymbol{\mu}_{\mathbf{s}}[1] > 0 \\
G_{verylow} + G_{copy}\times\lceil\boldsymbol{\mu}_{\mathbf{s}}[2] \div 32\rceil & \text{if} \quad w = \text{\small CALLDATACOPY} \> \lor \\
&\quad\text{\small CODECOPY} \lor \text{\small RETURNDATACOPY} \\
G_{extcode} + G_{copy}\times\lceil\boldsymbol{\mu}_{\mathbf{s}}[3] \div 32\rceil & \text{if} \quad w = \text{\small EXTCODECOPY} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1] & \text{if} \quad w = \text{\small LOG0} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+G_{logtopic} & \text{if} \quad w = \text{\small LOG1} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+2G_{logtopic} & \text{if} \quad w = \text{\small LOG2} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+3G_{logtopic} & \text{if} \quad w = \text{\small LOG3} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_{\mathbf{s}}[1]+4G_{logtopic} & \text{if} \quad w = \text{\small LOG4} \\
C_\text{\tiny CALL}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small CALL} \lor \text{\small CALLCODE} \> \lor \\
&\quad\text{\small DELEGATECALL} \\
C_\text{\tiny SELFDESTRUCT}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small SELFDESTRUCT} \\
G_{create} & \text{if} \quad w = \text{\small CREATE}\\
G_{create}+G_{sha3word} \lceil \mathbf{s}[2] \div 32 \rceil & \text{if} \quad w = \text{\small \hyperlink{create2}{CREATE2}}\\
G_{sha3}+G_{sha3word} \lceil \mathbf{s}[1] \div 32 \rceil & \text{if} \quad w = \text{\small SHA3}\\
G_{jumpdest} & \text{if} \quad w = \text{\small JUMPDEST}\\
G_{sload} & \text{if} \quad w = \text{\small SLOAD}\\
G_{zero} & \text{if} \quad w \in W_{zero}\\
G_{base} & \text{if} \quad w \in W_{base}\\
G_{verylow} & \text{if} \quad w \in W_{verylow}\\
G_{\mathrm{low}} & \text{if} \quad w \in W_{\mathrm{low}}\\
G_{mid} & \text{if} \quad w \in W_{mid}\\
G_{\mathrm{high}} & \text{if} \quad w \in W_{\mathrm{high}}\\
G_{extcode} & \text{if} \quad w = \text{\small EXTCODESIZE}\\
G_{extcodehash} & \text{if} \quad w = \text{\small \hyperlink{extcodehash}{EXTCODEHASH}}\\
G_{balance} & \text{if} \quad w = \text{\small BALANCE}\\
G_{blockhash} & \text{if} \quad w = \text{\small \hyperlink{blockhash}{BLOCKHASH}}\\
\end{cases}
\end{equation}
\begin{equation}
w \equiv \begin{cases} I_{\mathbf{b}}[\boldsymbol{\mu}_{\mathrm{pc}}] & \text{if} \quad \boldsymbol{\mu}_{\mathrm{pc}} < \lVert I_{\mathbf{b}} \rVert\\
\text{\small STOP} & \text{otherwise}
\end{cases}
\end{equation}

@@

&&&& Exactly equivalent to {\small \hyperlink{create2}{CREATE2}} except: \\
&&&& The salt $\zeta = \varnothing$ instead of $\boldsymbol{\mu}_{\mathbf{s}}[3]$. \\

@@

\linkdest{create2}{} 0xf5 & {\small CREATE2} & 4 & 1 & Create a new account with associated code. \\
&&&& $\zeta \equiv \boldsymbol{\mu}_{\mathbf{s}}[3]$ \\
&&&& $(\boldsymbol{\sigma}', \boldsymbol{\mu}'_{\mathrm{g}}, A^+, \mathbf{o}) \equiv \begin{cases}\Lambda(\boldsymbol{\sigma}^*, I_{\mathrm{a}}, I_{\mathrm{o}}, L(\boldsymbol{\mu}_{\mathrm{g}}), I_{\mathrm{p}}, \boldsymbol{\mu}_{\mathbf{s}}[0], \mathbf{i}, I_{\mathrm{e}} + 1, \zeta, I_{\mathrm{w}}) & \text{if} \quad \boldsymbol{\mu}_{\mathbf{s}}[0] \leqslant \boldsymbol{\sigma}[I_{\mathrm{a}}]_{\mathrm{b}} \; \\ \quad &\wedge\; I_{\mathrm{e}} < 1024\\ \big(\boldsymbol{\sigma}, \boldsymbol{\mu}_{\mathrm{g}}, \varnothing\big) & \text{otherwise} \end{cases}$ \\
&&&& is too low to fulfil the value transfer); and otherwise $x=A(I_{\mathrm{a}}, \boldsymbol{\sigma}[I_{\mathrm{a}}]_{\mathrm{n}}, \zeta, \mathbf{i} )$, the\\
&&&& address of the newly created account (\ref{eq:new-address}). \\
&&&& Thus the operand order is: value, input offset, input size, salt. \\
